Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2022-02-12 prevalence_testing/manual.tex
edits of manuscript and COP example

 \texttt{ps.indic.W.permanent(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl)} is a core function that produces the synthetic weights from \texttt{scm}, a sequence of $p$-values and corresponding rejection/acceptance decisions for each donor in the donor pool based on a give significance level and the test  function \texttt{taSPA.mhfc}. The assumed model for this function is
 \begin{align*}
 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \alpha_i I(t > T_i^*+1) + \varepsilon_{i,t},\\
 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
 \end{align*}
 where $T_i^*+1$ is the time point when the shock occurs for $i = 2, \ldots, n+1$, $\bs{x}_{i,t}$ is the covariate, and $\eta_i$ is the intercept. Note that only $\bs{\theta}$, $\eta_i$, and $\alpha_i$ are estimable. The above model is called permanent model due to the presence of a persistent shock term. For each donor, this function computes the adjusted forecast and unadjusted forecast, construct the corresponding loss differential matrix, and perform the forecast comparison test.  Suppose the donor pool size is $n$. \emph{It is important to note that the ordering of the donors should be with respect to the timing when those time series occur, from the earliest to the latest.}

 The input for this function is
\begin{itemize}
	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+2$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$. 
	\item \texttt{Y} is a list of responses with length $n +1$,  where the first element of the list should be the response of the time series of interest and the remaining elements of the list are the responses of the donors. It should be a vector.  Note  that to compute the lag, the effective sample size used is $T_i - 1$, where $T_i$ is the time series length of $i$th time series.
	\item \texttt{X} is a list of covariates with length $n+1$, where the first element of the list should be the covariates of the time series of interest and the remaining elements of the list are the covariates of the donors. The covariates should be in the class of \texttt{matrix} with size $T_i\times p$ for $i = 1, \ldots, n+1$. Note that the sample size of each element  in \texttt{X} should be  $T_i+ K_i + H$, where $K_i$ is the training sample size and $T_i$ is the length of the donor time series that are wished to be considered as the data used in forecast comparison. $H$ is the maximum horizon.
	\item \texttt{K} is a vector of training sample sizes that are used to compute $h$-step forecast for each data point. \texttt{K} has a length of $n+1$. If \texttt{retro = FALSE}, \texttt{K[1]} can be \texttt{NA}.
	\item \texttt{H} is the maximum $h$ that an $h$-step forecast that is wished to be considered in the multi-horizon forecast comparison testing procedure in \citeA{quaedvlieg2021multi}.
	\item \texttt{Ts} is a vector of length $n+1$, and it specifies the length of the time series (ordered from the time series of interest to donors). Note that for each element of \texttt{Ts}, it should be at least greater than or equal to $K_i + H + 2$.
	\item \texttt{ell} is the block length of the moving block bootstrap. See details in \texttt{taSPA.mhfc}.
	\item \texttt{B} is the bootstrap sample size. See details in \texttt{taSPA.mhfc}.
	\item \texttt{bw} is the bandwidth of computation for HAC estimator. See details in \texttt{taSPA.mhfc}.
	\item \texttt{sig.levl} is the significance level for the test. It is 0.05 in default.
	\item \texttt{retro} is a logical value indicating \texttt{TRUE} or \texttt{FALSE}. If  \texttt{TRUE}, the $p$-value for the time series of interest will be computed. If  \texttt{FALSE}, only the $p$-values of donors will be computed. This argument is intended for retrospective data analysis where the $p$-value of the time series of interest is needed.
	\item \texttt{scale} option can allow users to compute weights based on scaled covariates or not. See details in \texttt{scm}.
\end{itemize}

@@

 \texttt{ps.indic.W.dynamic(Tstar,Y,X,K,H,Ts,q1,q2,ell,B,bw,sig.levl)} performs the similar functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
 \begin{align*}
 	y_{i,t}
 	&= \left(\eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
 	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i}
 \end{align*}
 where $D_{i,t}=I(t > T_i^*+1)$. Note that only $\eta_i, \alpha_i - \eta_i, \phi_{i,j}, \bs{\theta}_{i, j+1}, \tilde{\phi}_{i,j}-\phi_{i,j}, \tilde{\bs{\theta}}_{i,j+1}-\bs{\theta}_{i, j+1}$ are estimable.
The role of the shock in this model is that the dynamics of $y_{i,t}$ change after the shock. Note that to prepare the lagged response and covariates, the effective sample size is $T_i-\max\{q_1, q_2-1\}$.  Note that for each element of \texttt{Ts}, it should be at least greater than or equal to $K_i + H + \max\{q_1, q_2-1\}+1$.

>>>>

 \texttt{ps.indic.W.permanent(Tstar,Y,X,K,H,Ts,ell,B,bw,sig.levl,retro,q1,selfW)} is a core function that produces the synthetic weights from \texttt{scm}, a sequence of $p$-values and corresponding rejection/acceptance decisions for each donor in the donor pool based on a give significance level and the test  function \texttt{taSPA.mhfc}. The assumed model for this function is
 \begin{align*}
 	y_{i,t} &= \eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j}  +\sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1}  + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
 \end{align*}
 where $T_i^*+1$ is the time point when the shock occurs for $i = 2, \ldots, n+1$, $\bs{x}_{i,t}$ is the covariate, and $\eta_i$ is the intercept. Note that only $\bs{\theta}$, $\eta_i$, and $\alpha_i$ are estimable. The above model is called permanent model due to the presence of a persistent shock term. For each donor, this function computes the adjusted forecast and unadjusted forecast, construct the corresponding loss differential matrix, and perform the forecast comparison test.  Suppose the donor pool size is $n$. \emph{It is important to note that the ordering of the donors should be with respect to the timing when those time series occur, from the earliest to the latest.}

 The input for this function is
\begin{itemize}
	\item \texttt{Tstar} is a vector of shock-effect time points when the shock occurs at $T^*_i+2$ for $i = 1, \ldots, n+1$. The size of \texttt{Tstar} should be $n+1$. 
	\item \texttt{Y} is a list of responses with length $n +1$,  where the first element of the list should be the response of the time series of interest and the remaining elements of the list are the responses of the donors. It should be a vector.  Note  that to compute the lag, the effective sample size used is $T_i - 1$, where $T_i$ is the time series length of $i$th time series.
	\item \texttt{X} is a list of covariates with length $n+1$, where the first element of the list should be the covariates of the time series of interest and the remaining elements of the list are the covariates of the donors. The covariates should be in the class of \texttt{matrix} with size $T_i\times p$ for $i = 1, \ldots, n+1$. Note that the sample size of each element  in \texttt{X} should be  $T_i+ K_i + H$, where $K_i$ is the training sample size and $T_i$ is the length of the donor time series that are wished to be considered as the data used in forecast comparison. $H$ is the maximum horizon.
	\item \texttt{K} is a vector of training sample sizes that are used to compute $h$-step forecast for each data point. \texttt{K} has a length of $n+1$. If \texttt{retro = FALSE}, \texttt{K[1]} can be \texttt{NA}.
	\item \texttt{H} is the maximum $h$ that an $h$-step forecast that is wished to be considered in the multi-horizon forecast comparison testing procedure in \citeA{quaedvlieg2021multi}.
	\item \texttt{Ts} is a vector of length $n+1$, and it specifies the length of the time series (ordered from the time series of interest to donors). Note that for each element of \texttt{Ts}, it should be at least greater than or equal to $K_i + H + 2$.
	\item \texttt{ell} is the block length of the moving block bootstrap. See details in \texttt{taSPA.mhfc}.
	\item \texttt{B} is the bootstrap sample size. See details in \texttt{taSPA.mhfc}.
	\item \texttt{bw} is the bandwidth of computation for HAC estimator. See details in \texttt{taSPA.mhfc}.
	\item \texttt{sig.levl} is the significance level for the test. It is 0.05 in default.
	\item \texttt{retro} is a logical value indicating \texttt{TRUE} or \texttt{FALSE}. If  \texttt{TRUE}, the $p$-value for the time series of interest will be computed. If  \texttt{FALSE}, only the $p$-values of donors will be computed. This argument is intended for retrospective data analysis where the $p$-value of the time series of interest is needed.
	\item \texttt{scale} option can allow users to compute weights based on scaled covariates or not. See details in \texttt{scm}.
	\item \texttt{q1} specifies the number of lags for the response.
\end{itemize}
Note that the specification $q_2$ is not considered in this function as users can just include them in the covariates and this step does not influence the computation of the function.

@@

 \texttt{ps.indic.W.dynamic(Tstar,Y,X,K,H,Ts,q1,q2,ell,B,bw,sig.levl)} performs the similar functionality as  \texttt{ps.indic.W.permanent} but with a different model as 
\begin{align*}
 	y_{i,t}
 	&= \left(\eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
 	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
 \end{align*}
 where $D_{i,t}=I(t > T_i^*+1)$. Note that only $\eta_i, \alpha_i - \eta_i, \phi_{i,j}, \bs{\theta}_{i, j+1}, \tilde{\phi}_{i,j}-\phi_{i,j}, \tilde{\bs{\theta}}_{i,j+1}-\bs{\theta}_{i, j+1}$ are estimable.
The role of the shock in this model is that the dynamics of $y_{i,t}$ change after the shock. Note that to prepare the lagged response and covariates, the effective sample size is $T_i-\max\{q_1, q_2-1\}$.  Note that for each element of \texttt{Ts}, it should be at least greater than or equal to $K_i + H + \max\{q_1, q_2-1\}+1$.

### 2022-02-12 prevalence_testing/postshocktest2021draft.tex
minor edits
edits of manuscript and COP example

As illustrated in Section 5.1 in \cite{lin2021minimizing}, it is found that Conoco Phillips stock price experienced unprecedented shocks due to  oil supply control and COVID-19 pandemic on one single day,  March 9th, 2020. In this data example, we are interested in investigating whether this shock is prevalent, i.e., whether the impact of the shock on the stock price will persist over time. Denote the stock price of Conoco Phillips at time $t$ as $y_{i,t}$ for $i$th time series, where $i = 1, \ldots n+1$, the time series of interest is ordered as the 1st time series, and $n$ is the donor pool size. We used the same covariates  as \cite{lin2021minimizing} did in the model of $y_{i,t}$, which are S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, and 13-week treasury bill rates.

@@

To analyze the dataset, we propose two models. Denote the covariate matrix at time $t$ for $i$th time series by $\bs{x}_{i,t}$.  The first model $\mc{M}_1$, called ``permanent'' model, is 
 \begin{align*}
 	y_{i,t} &= \eta_i + \phi_i y_{i, t-1}  + \bs{x}_{i, t}\bs{\theta} + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
 \end{align*}
where $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$ and $t = 1, \ldots, T_i$. Note that we allow the shock effect to take effect for multiple time points instead of one time point as in  \cite{lin2021minimizing}. This simple model describes the setting where one additive shock effect is persistent over time. The second model $\mc{M}_2$, called ``dynamic'' model, is
\begin{align*}
 	y_{i,t}
 	&= \left(\eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
 	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
 	\alpha_i & = \mu_{\alpha} + \bs{x}_{i, T_i^*+1} + \varepsilon_{\alpha, i},
 \end{align*}
 where $q_1 = q_2=2$,  $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$, and $t = 1, \ldots, T_i$. We estimate $\mc{M}_1$ and $\mc{M}_2$ using ordinary least squares (OLS) estimation. $\mc{M}_2$ adds more flexibility to $\mc{M}_1$ by allowing that the model of $y_{i,t}$ changes after the shock, as seen from the term related to $1-D_{i,t}$,  though the model still preserves the autoregressive model form. In practice, $\mc{M}_2$ should make more sense than $\mc{M}_1$ as it accommodates for more complicated cases. However, $\mc{M}_2$  requires far more degrees of freedom for estimation and this can increase variance in estimation. We used weighted AIC for model selection, which is detailed as follows. For $i$th donor in the donor pool, we can compute its AICs for $\mc{M}_1$ and $\mc{M}_2$, say $a^1_i$ and $a^2_i$, and also its synthetic weight $W_i^*$, where $\mbf{W}^* = (w_2^*, \ldots, w_{n+1}^*)$ and its computation is detailed in the next paragraph. Let $A^{1*}= \sum_{i=2}^{n+1} w_i^* a^1_i$ and $A^{2*}= \sum_{i=2}^{n+1} w_i^*a^2_i$. We will select $\mc{M}_1$ if $A^{1*} < A^{2*}$ and vice versa.

 In computing the weights, to avoid the impact of unit differences from different columns of covariates on weighting, we center and scale the covariates. The steps are detailed as below. Consider
\begin{align*}
	\bs{X}= \begin{pmatrix}
		\bs{x}_{1, T_1^*+1}\\
		\vdots  \\
		\bs{x}_{n+1, T_{n+1}^*+1}
	\end{pmatrix},
\end{align*}
where $t = T_i^*+1$ is the time point when the shock effect takes place for $i$th time series. For each column of $\bs{X}$, we center it by subtracting its column mean and scale the resulting column vector by dividing the standard deviation of the resulting column vector. Denote the resulting covariates matrix by $\bs{X}^*$. We compute the synthetic weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}. However, for the model of $y_{i,t}$, we do not conduct such centering and scaling procedure.

@@

\begin{table}[H]
	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.221, 0, 0.779)$ from scaled covariates} \label{coptable}
\begin{center}
  \begin{tabular}{cccccccccr}
     $L$  & Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     7 & $\mc{M}_1$  & $289.61$ & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
     7 & $\mc{M}_2$  & 420.86 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
     15 & $\mc{M}_1$ & 294.74 & 1   & 0 &0 (Yes) & 0 (Yes)     \\
     15 &  $\mc{M}_2$ & $416.12$ & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
     30 &  $\mc{M}_1$ & 303.88 & 1   & $0$ & 0 (Yes) &0 (Yes)   \\
     30 &  $\mc{M}_2$ & 435.22 & 1  & 0 &0 (Yes) & 0 (Yes)  
  \end{tabular}
\end{center}	
\end{table}

@@

Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.221, 0, 0.779)$. It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second. As pointed out by \cite{lin2021minimizing} in Section 5.1(3), the shocks experienced by the first and  third donor are related to recessions, and oil supply shock, respectively. The results are intuitive in the sense that from a retrospective perspective of a data analyst, the shock experienced by the series $\{y_{1,t}\colon t = 1, \ldots, T_1\}$ is due to oil supply shock and recessions caused by COVID-19 pandemic.

Additionally, from Table \ref{coptable}, for all $L = 7, 15, 30$, $\mc{M}_1$ is preferred over $\mc{M}_2$. Nevertheless, the inference results of  $\mc{M}_1$  do not differ from $\mc{M}_2$, as seen from the fourth column to the seventh column of Table \ref{coptable}. It is possible that   $\mc{M}_2$ is also a good fit for the dataset.

It is important to note that $p_1$ is the $p$-value of the forecast comparison between adjusted forecast and unadjusted forecast if we have the data $\{y_{1,t} \colon 1, \ldots, T_1\}$, where $T_1 > T_1^*$. In other words, it cannot be computed without observing $y_{1, t}$ for $t > T_1^*$ and we present $p_1$ only for retrospective analysis. Also, $\hat{p}$ is the $p$-value from weighting the $p$-values of the forecast comparison  between adjusted and unadjusted forecast for donors using $\mbf{W}^*$. Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and models. It suggests $\hat{p}$ turns out to be a good estimate of $p_1$; and the test  using $\hat{p}$ fails to reject that  the shock, which was to take effect at $t=T_1^*+1$,  is prevalent for $t > T_1^*+1$ under a significance level of 5\%.

Recall from Section \ref{forecast}, voting procedure suggests shock transience (shock prevalence) if the majority of the tests  suggests shock transience (shock prevalence, respectively). We record 0 if the voting procedure suggests shock transience and 1 if shock prevalence. The weighted voting procedure weight those testing indicators using $\mbf{W}^*$; and returns shock prevalence if the output exceeds 0.5 and shock transience if the output is smaller than 0.5. As we observe $\{y_{1,t} \colon 1, \ldots, T_1\}$, we are able to check whether the decision of voting and weighted voting is correct. From the sixth and seventh columns of Table \ref{coptable}, we can see that voting and weighted voting procedures suggest shock transience and this decision is consistent across different $L$ and different models. As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small. Note that Proposition \ref{votprop} and Corollary \ref{coro1} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$.

@@

>>>>

As illustrated in Section 5.1 in \cite{lin2021minimizing}, it is found that Conoco Phillips stock price experienced unprecedented shocks due to  oil supply control and COVID-19 pandemic on one single day,  March 9th, 2020. In this data example, we are interested in investigating whether this shock is prevalent, i.e., whether the impact of the shock on the stock price will persist over time. Denote the stock price of Conoco Phillips at time $t$ as $y_{i,t}$ for $i$th time series, where $i = 1, \ldots n+1$, the time series of interest is ordered as the 1st time series, and $n$ is the donor pool size. In the model of $y_{i,t}$, the covariates we consider are S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13-week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX).

@@

To analyze the dataset, we propose two models. Denote the covariate matrix at time $t$ for $i$th time series by $\bs{x}_{i,t}$.  The first model $\mc{M}_1$, called ``permanent'' model, is 
 \begin{align*}
 	y_{i,t} &= \eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j}  +\sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1}  + \alpha_i  D_{i,t}+ \varepsilon_{i,t},\\
 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
 \end{align*}
where $q_1 = q_2=2$, $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$ and $t = 1, \ldots, T_i$. Note that we allow the shock effect to take effect for multiple time points instead of one time point as in  \cite{lin2021minimizing}. This simple model describes the setting where one additive shock effect is persistent over time. The second model $\mc{M}_2$, called ``dynamic'' model, is
\begin{align*}
 	y_{i,t}
 	&= \left(\eta_i + \sum_{j=1}^{q_1} \phi_{i,j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j}\bs{\theta}_{i, j + 1} \right) (1-D_{i,t}) + f(\mc{F}_{i, t} \alpha_i)D_{i,t} + \varepsilon_{i,t}  \\
 	f(\mc{F}_{i,t},\alpha_i)	 & = \alpha_i +\sum_{j=1}^{q_1} \tilde{\phi}_{i, j} y_{i, t-j} + \sum_{j=0}^{q_2-1} \bs{x}_{i, t-j} \tilde{\bs{\theta}}_{i, j +1} \\
 	\alpha_i & = \mu_{\alpha} + \sum_{j=0}^{q_2-1} \bs{x}_{i, T_i^*+1-j}\bs{\delta}_{i, j + 1} + \varepsilon_{\alpha, i},
 \end{align*}
 where $q_1 = q_2=2$,  $D_{i,t} = I(t > T_i^*+1)$, $i = 1, \ldots, n+1$, and $t = 1, \ldots, T_i$. We estimate $\mc{M}_1$ and $\mc{M}_2$ using ordinary least squares (OLS) estimation. $\mc{M}_2$ adds more flexibility to $\mc{M}_1$ by allowing that the model of $y_{i,t}$ changes after the shock, as seen from the term related to $1-D_{i,t}$,  though the model still preserves the autoregressive model form. In practice, $\mc{M}_2$ should make more sense than $\mc{M}_1$ as it accommodates for more complicated cases. However, $\mc{M}_2$  requires far more degrees of freedom for estimation and this can increase variance in estimation. We used weighted AIC for model selection, which is detailed as follows. For $i$th donor in the donor pool, we can compute its AICs for $\mc{M}_1$ and $\mc{M}_2$, say $a^1_i$ and $a^2_i$, and also its synthetic weight $W_i^*$, where $\mbf{W}^* = (w_2^*, \ldots, w_{n+1}^*)$ and its computation is detailed in the next paragraph. Let $A^{1*}= \sum_{i=2}^{n+1} w_i^* a^1_i$ and $A^{2*}= \sum_{i=2}^{n+1} w_i^*a^2_i$. We will select $\mc{M}_1$ if $A^{1*} < A^{2*}$ and vice versa.

 In computing the weights, to avoid the impact of unit differences from different columns of covariates on weighting, we center and scale the covariates. The steps are detailed as below. Consider
\begin{align*}
	\bs{X}= \begin{pmatrix}
		\bs{x}_{1, T_1^*+1} & \bs{x}_{1, T_1^*}\\
		\vdots & \vdots  \\
		\bs{x}_{n+1, T_{n+1}^*+1} & \bs{x}_{1, T_1^*}
	\end{pmatrix},
\end{align*}
where $t = T_i^*+1$ is the time point when the shock effect takes place for $i$th time series. Note that the reason for including $\bs{x}_{i, T_i^*}$ is that we consider $q_2=2$ in $\mc{M}_1$ and $\mc{M}_2$. In other words, the consider the 1-step lagged covariates in the model and its corresponding shock effect time point is $T_i^*$. For each column of $\bs{X}$, we center it by subtracting its column mean and scale the resulting column vector by dividing the standard deviation of the resulting column vector. Denote the resulting covariates matrix by $\bs{X}^*$. We compute the synthetic weights $\mbf{W}^*$  based on $\bs{X}^*$ according to procedures detailed in Section 2.2 of \cite{lin2021minimizing}. However, for the model of $y_{i,t}$, we do not conduct such centering and scaling procedure.

@@

\begin{table}[H]
	\caption{Results for Conoco Philips ($n=3$), $\mbf{W}^* = (0.183, 0, 0.817)$ from scaled covariates} \label{coptable}
\begin{center}
  \begin{tabular}{cccccccccr}
     $L$  & Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     7 & $\mc{M}_1$  & $214.10$ & 1  & 0 & 0 (Yes) &0 (Yes)  \\      
     7 & $\mc{M}_2$  & 205.23 & 1 & $0$   & 0 (Yes) &0 (Yes)   \\[.2cm]
     15 & $\mc{M}_1$ & 246.67 & 1   & $0.82$ & 0 (Yes) &1 (No)    \\
     15 &  $\mc{M}_2$ & $238.24$ & 1 & 0 &0 (Yes)  &0 (Yes)  \\[.2cm]
     30 &  $\mc{M}_1$ & 303.43 & 1   & $0.82$ & 0 (Yes) &1 (No)   \\
     30 &  $\mc{M}_2$ & 293.38 & 1  & 0 &0 (Yes) & 0 (Yes)  
  \end{tabular}
\end{center}	
\end{table}

@@

Note that the synthetic weight vector $\mbf{W}^*$ for the three donors is $(0.183, 0, 0.817)$. It suggests that the donor associated with the shock on November 27, 2014 is the most similar time series relative to the time series of interest, and the one on March 15, 2008 is the second. As pointed out by \cite{lin2021minimizing} in Section 5.1(3), the shocks experienced by the first and  third donor are related to recessions, and oil supply shock, respectively. The results are intuitive in the sense that from a retrospective perspective of a data analyst, the shock experienced by the series $\{y_{1,t}\colon t = 1, \ldots, T_1\}$ is due to oil supply shock and recessions caused by COVID-19 pandemic.

In term of Table \ref{coptable}, it is important to note that $p_1$ is the $p$-value of the forecast comparison between adjusted forecast and unadjusted forecast if we have the data $\{y_{1,t} \colon 1, \ldots, T_1\}$, where $T_1 > T_1^*$. In other words, it cannot be computed without observing $y_{1, t}$ for $t > T_1^*$ and we present $p_1$ only for retrospective analysis. Also, $\hat{p}$ is the $p$-value from weighting the $p$-values of the forecast comparison  between adjusted and unadjusted forecast for donors using $\mbf{W}^*$. From Table \ref{coptable}, for all $L = 7, 15, 30$, $\mc{M}_2$ is preferred over $\mc{M}_1$. Notice that $|\hat{p}-p_1|$ is uniformly zero and $p_1$ is uniformly 1 for different $L$ and $\mc{M}_2$. The test  using $\hat{p}$ with $\mc{M}_2$ fails to reject that  the shock, which was to take effect at $t=T_1^*+1$,  is prevalent for $t > T_1^*+1$ under a significance level of 5\%. Nevertheless, the results appear to be a little different for $\mc{M}_1$. For $L=7$, $|\hat{p}-p_1|=0$ for $\mc{M}_1$ whereas $|\hat{p}-p_1|=0.82$ for $L = 15, 30$. Based on the performance of $\mc{M}_2$, it is possible that as the time window $L$ increases, the signal from changing parameters covariates is ``misunderstood'' by $\mc{M}_1$ as shock signal.

Recall from Section \ref{forecast}, voting procedure suggests shock transience (shock prevalence) if the majority of the tests  suggests shock transience (shock prevalence, respectively). We record 0 if the voting procedure suggests shock transience and 1 if shock prevalence. The weighted voting procedure weight those testing indicators using $\mbf{W}^*$; and returns shock prevalence if the output exceeds 0.5 and shock transience if the output is smaller than 0.5. As we observe $\{y_{1,t} \colon 1, \ldots, T_1\}$, we are able to check whether the decision of voting and weighted voting is correct. From the sixth column of Table \ref{coptable}, we can see that voting procedure suggests shock transience for $\mc{M}_1$ and $\mc{M}_2$ for different $L$. However, weighted voting suggests shock transience for $\mc{M}_2$ for different $L$ but shock prevalence for $\mc{M}_1$ and $L=15, 30$ and shock transience for $\mc{M}_1$ and $L = 7$. As $p_1$ is uniformly 1, it is reasonable to expect $\P(p_1\leq .05)$ be small. Note that Proposition \ref{votprop} and Corollary \ref{coro1} show that the decisions made by voting and weighted voting procedures should be correct with very high probability if we assume the asymptotic approximation of the expected absolute error works well for  $n = 3$. Note that the interpretation and meaning of $p_1$ is closely connected with models. For example, $\mc{M}_1$ would imply a persistent shock whereas $\mc{M}_2$ is more general in suggesting changing dynamics. Thus, even if  this theoretical statement  may be correct, it makes practical sense only when model is identified well. This comment corresponds to the possibility that $\mc{M}_1$ may ``misunderstand'' the wrong signal of changing dynamics that are instead captured by $\mc{M}_2$.

@@

\subsection{Testing shock prevalence for persons on nonfarm payrolls}

\begin{table}[H]
	\caption{Results for persons on nonfarm payrolls ($n=3$), $\mbf{W}^* = (0, 0.278, 0.722)$ from scaled covariates} \label{uemtable}
\begin{center}
  \begin{tabular}{ccccccccr}
      Model & weighted  AIC & $p_1$ &  $|\hat{p}-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     $\mc{M}_1$  & $-687.836$ & 0  & 1 & 1 (No) &1 (No)  \\      
      $\mc{M}_2$ ($q_1=q_2=1$)  & $-688.428$ & 0.470 & $0.146$   & 0 (Yes) &0 (Yes)   \\[.2cm]
  \end{tabular}
\end{center}	
\end{table}

\begin{figure}[H]
	\begin{center}
		\includegraphics[height = 8cm]{UEMtransience.pdf}
		\caption{The shock transience of $\{y_{1,t} \colon 1, \ldots, T_1\}$} \label{uemshocktransience}
	\end{center}	
\end{figure}
